Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-21 mpaper/paper.tex
The abstract

\begin{abstract}
  We prove the validity of performing variational inference on the Gaussian
  process-based inverse reinforcement learning model that preserves and
  approximates the full joint probability distribution of rewards across states
  of the Markov decision process.%TODO: finish this.
  According to Simon Peyton Jones, an abstract should address
  four key questions. First, what is the problem that this
  paper tackles? Second, why is this an interesting problem?
  Third, what is the solution this paper proposes?
  Finally, why is the proposed solution a good one?
\end{abstract}

>>>>

\begin{abstract}
  The inverse reinforcement learning (IRL) problem asks us to find a reward
  function of a Markov decision process that explains observed behaviour. Many
  approaches are only able to construct reward functions as linear combinations
  of state features. Out of those that can handle nonlinearity, none can provide
  a full posterior distribution of rewards. Providing variance estimates for
  rewards would allow one to judge how well the model has learned its policy and
  discover any weak spots the model may have. We show how to perform variational
  inference (VI) on a Gaussian process-based IRL model in order to approximate
  the posterior distribution of rewards. We prove the correctness of the
  approach and demonstrate the model's behaviour in practice. Being able to
  provide full posterior probability distributions in IRL unlocks many new
  research frontiers ranging from integrating recent developments in VI to make
  the models more efficient and flexible, to developing complex reinforcement
  learning agents that can explicitly search for opportunities to fix their
  weaknesses.
\end{abstract}
